Identifying Departures from the Fully Developed Speckle Hypothesis in Intensity SAR Data with Non-Parametric Estimation of the Entropy

### 2024-01-14 Text/Articles/MIGARS_2024/R1-The Entropy as a Proxy for Fully Developed Speckle.Rmd
Small format detail
paper updates and empirical densities

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=TRUE)
library(ggplot2)
library(reshape2)
#library(plotly)
library(knitr)
library(pandoc)
library(gridExtra)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(rmutil)
library(invgamma)
library(tidyverse)
library(RColorBrewer)
library(ggsci)
#library(wesanderson)
library(ggpubr)
library(patchwork)
library(dplyr)
#options(kableExtra.latex.load_packages = FALSE)
library(devtools)
#devtools::install_github("haozhu233/kableExtra")
library(kableExtra)
library(ggthemes)
library(latex2exp)

@@

Fig.&nbsp;\ref{fig:3d_GIO} illustrates the entropy of $G_I^0$ distribution as a function of three key parameters: $\mu$, $\alpha$, and $L$.

```{r 3d_GIO, fig.align="center",  out.width = "70%", fig.cap="The Shannon Entropy under ${G}_I^0$ models.", fig.show="hold",  fig.pos="hbt"}
knitr::include_graphics("../../../Figures/PDF/entropy_plot_3d.pdf")
```
As we explore the 3D plot, we can observe how changes in $\mu$, $\alpha$, and $L$ collectively influence the entropy of the $G_I^0$ distribution. 
We can identify regions where entropy is high or low, providing insights into the predictability and structure of the distribution in various regions of the parameter space.

@@

```{r Plot_GI0_to_gamma, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ as $\\alpha$ takes large negative values and $L=5$."}

L <- c(5)
alphas <- c(  -3, -8, -20, -1000)
alpha_labels <- c( expression(italic(alpha) == -3), expression(italic(alpha) == -8), expression(italic(alpha) == -20), expression(italic(alpha) == -1000))

@@

```{r Plot_empirical, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Empirical distributions of $\\Gamma_{\\text{SAR}}$ and $G_I^0$ entropies as $\\mu=1$, $L=5$ and $\\alpha\\in\\{-1000, -20, -8, -3\\}$."}

@@

R <- 3000
mu <- 1
L <- 5
B <- 1
sample.size <- c( 121)

@@

      #TestStat1[r] <- log(mean(z))  - (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))
      #TestStat2[r] <- -bootstrap_correa_estimator_log_mean(z, B) - (-L + log(L) - lgamma(L) - (1 - L) * digamma(L) + L + lgamma(L - alpha1) - (L - alpha1) * (digamma(L - alpha1)) + (1 - alpha1) * digamma(-alpha1) - log(-1 - alpha1) - lgamma(-alpha1))
    }

    # mean_entropy1[sample.size == s] <- mean(TestStat1)
    # #cat(" mean for TestStat1", mean_entropy1[sample.size == s], "\n")
    # 
    # mean_entropy2[sample.size == s] <- mean(TestStat2)
    # cat(" mean for TestStat2", mean_entropy2[sample.size == s], "\n")

@@

$$
 \begin{cases}\mathcal{H}_0: \mathcal{D}(\bm{\theta})=\Gamma_{\text{SAR}} \\ 
  \mathcal{H}_1: \mathcal{D}(\bm{\theta})=G_I^0.\end{cases}
$$
In other words, we verify the hypothesis that the data are fully-developed speckle.
<!-- \begin{align*} -->
<!-- \mathcal{H}_1 &: T_{\mathcal{D}}\neq D_0,\\  -->
<!-- \mathcal{H}_1 &: T_{\mathcal{D}}> D_0,\text{ or}\\ -->
<!-- \mathcal{H}_1 &: T_{\mathcal{D}}< D_0.  -->
<!-- \end{align*} -->
For this purpose, we use the following test statistic:
\begin{equation}
\label{Eq:test_e}
S(Z)= \widetilde{H}(Z)-H(Z).
\end{equation}
This test statistic $S(Z)$ aims to assess the behavior of the data under the null hypothesis, through the empirical distribution of the test statistic values for a sample size of $n$. The density should center around zero if the test statistic is capable of detecting that the data are fully-developed speckle, i.e., $S(Z)\approx 0$. Otherwise, under the alternative hypothesis, the empirical distribution of the test statistic values is not centered around zero. This suggests significant differences and implies the presence of heterogeneous clutter.

<!-- so the null hypothesis should be rejected if (i) $Z_{n,m} > z_{\alpha/2}$ or $Z_{n,m} < - z_{\alpha/2}$ for $\Phi_{\mathcal N}(z_{\alpha/2})=1-\alpha/2$ and $\Phi_{\mathcal N}$ being the standard normal cumulative distribution function, (ii) $Z_{n,m} > z_{\alpha/2}$ or (iii) $Z_{n,m} < - z_{\alpha/2}$.   -->

@@

estimators_to_plot <- c("Correa", "Ebrahimi", "Al Omari",  "Correa Bootstrap", "Ebrahimi Bootstrap", "Al Omari Bootstrap" )
  latex_estimator_names <- c("Correa" = expression("$\\widehat{italic(H)}_{C}$"),#parse(text=TeX("$H_{2}$")),
                             "Correa Bootstrap" = expression("$\\widetilde{italic(H)}_{C}$"),
                            "Ebrahimi" = expression("$\\widehat{italic(H)}_{E}$"),
                            "Al Omari" = expression("$\\widehat{italic(H)}_{AO}$"),
                            "Ebrahimi Bootstrap" = expression("$\\widetilde{italic(H)}_{E}$"),
                            "Al Omari Bootstrap" = expression("$\\widetilde{italic(H)}_{AO}$"))
selected_estimators_latex <- latex_estimator_names[estimators_to_plot]

@@

colnames(reshaped_results) <- c("$\\bm{\\mu}$", "$\\bm{n}$", "$\\widetilde{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{E}}$", "$\\widetilde{H}_{\\text{AO}}$", "$\\widetilde{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{E}}$", "$\\widetilde{H}_{\\text{AO}}$")

#
print(
  kbl(
    reshaped_results,
    caption = "Bias and MSE of bootstrap estimators for $G_I^0$, $L=8$, $\\alpha=-20$.",
    format = "latex",
    booktabs = TRUE,
    align = "c",
    escape = FALSE, 
    digits = 4,  
    label = "table2"  
  ) %>%
    add_header_above(c(" ", " ", "Bias" = 3, "MSE" = 3)) %>%
    collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle")
)
```

```{r Simulated_data_test_gi0, echo=FALSE, message=FALSE}

set.seed(1234567890, kind = "Mersenne-Twister")
sample_sizes <- c(9, 25, 49, 81, 121)
# Number of replications para simulacion montecarlo para calculo de error tipo 1

N <- 1000

# Number of replications para calcular las entropias
R <- 10

# Number of bootstrap replications
B <- 10
mu_values <- c(5)
alpha <- -1000
L <- 2

  estimators <- list(
    #"Correa" = correa_estimator,
    "$\\widetilde{H}_{C}$ " = bootstrap_correa_estimator,
    "$\\widetilde{H}_{E}$ " = bootstrap_ebrahimi_estimator,
    "$\\widetilde{H}_{AO}$ " = bootstrap_al_omari_1_estimator
  )

calculate_results_test_gi0 <- function(sample_sizes, R, B, mu_values, alpha, L, estimators) {
  results_list <- list()

    results <- calculate_entropy_and_test(sample_sizes, R, B, mu_val, alpha, L, estimators)
    df <- as.data.frame(results)

results_gi0_1 <- calculate_results_test_gi0(sample_sizes, R, B, mu_values, alpha, L, estimators)

save(results_gi0_1, file = "./Data/results_gi0_1.Rdata")

@@

```{r Table_test_gi0, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

load("./Data/results_gi0_1.Rdata")

for (mu_val in mu_values) {
  results_data <- results_gi0_1[[as.character(mu_val)]]

  table_result <- kbl(
    results_data,
    caption = paste("Hypothesis Testing for $G_I^0$, $\\mu =", mu_val, "$, $L=2$, $\\alpha=-1000$ , $H_{\\Gamma_{\\text{SAR}}}=2.493$."),
    format = "latex",
    booktabs = TRUE,
    align = "c",
    escape = FALSE,
    digits = 4,
    label = "table_hipotesis"
    #label = paste("table_hipotesis", mu_val, sep = "")
  ) %>%
    collapse_rows(columns = 1:3, latex_hline = "major", valign = "middle")

  print(table_result)
}

@@

  plot <- ggplot(TestStatistics1, aes(x = Test_Statistics)) +
    geom_line(aes(col = factor(Sample_Size), linetype = factor(Sample_Size)), stat = "density", linewidth = 1.0) +
    geom_line(data = TestStatistics2, aes(x = Test_Statistics2), stat = "density", color = "blue", linetype = "dashed", linewidth = 1) +
    geom_vline(xintercept = difference.betweeen.GammaSAR.GI0.n.Look(-8, 5), col="darkgreen", linetype = "dotted", linewidth = 0.6) +
    annotate("text", x=difference.betweeen.GammaSAR.GI0.n.Look(-8, 5), y=7, parse=TRUE, label="alpha==-8", hjust=-.1, vjust=1.0, col="darkgreen") +
   # geom_vline(xintercept = difference.betweeen.GammaSAR.GI0.n.Look(-20, 5), col="darkgreen", linetype = "dotted", linewidth = 0.6) +
   # annotate("text", x=difference.betweeen.GammaSAR.GI0.n.Look(-20, 5), y=7, parse=TRUE, label="alpha==-20", hjust=-.1, vjust=2.0, col="darkgreen") +
    geom_vline(xintercept = difference.betweeen.GammaSAR.GI0.n.Look(-1000, 5), col="darkgreen", linetype = "dotted", linewidth = 0.6) +
    #annotate("text", x=difference.betweeen.GammaSAR.GI0.n.Look(-1000, 5), y=7, parse=TRUE, label="alpha==-1000", hjust=-.1, vjust=4.0, col="darkgreen") +
    labs(x = "Test Statistics", y = "Empirical Density") +
    #annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("alpha == %s", alpha_val)), hjust = 1.2, vjust = 1.02, size = 3) +
    theme_minimal() +
    theme(
      text = element_text(family = "serif"),
      legend.position = "none"  
    )

@@

A hypothesis testing was conducted using non-parametric entropy estimators as test statistics. 
The results in Table&nbsp;\ref{tab:table_hipotesis} show that data from the $G_I^0$ distribution exhibit fully developed speckle behavior, specifically in the limit case with parameters $\mu=5$, $L=2$, and $\alpha= -1000$. 
The true entropy of $\Gamma_{\text{SAR}}$ was set at $H_{\Gamma_{\text{SAR}}} = 2.493$.  
It is observed that, for different sample sizes, entropy values converge towards the true value of the Gamma SAR distribution.

```{r Simulated_data_test_gi0_2, echo=FALSE, message=FALSE}

set.seed(1234567890, kind = "Mersenne-Twister")
sample_sizes <- c(49, 81, 121)
N<- 100
# Number of replications
R <- 100

# Number of bootstrap replications
B <- 2
mu_values <- c(1)
alpha <- -600
L <- 5

  estimators <- list(

    "$\\widetilde{H}_{C}$ " = bootstrap_correa_estimator
    #"$\\widetilde{H}_{E}$ " = bootstrap_ebrahimi_estimator,
    #"$\\widetilde{H}_{AO}$ " = bootstrap_al_omari_1_estimator
  )
 #true_entropy <- entropy_gamma_sar(L, mu) 
calculate_entropy_and_test_montecarlo <- function(sample_sizes, R, N, B, mu, alpha, L, estimators, true_entropy) {
  true_entropy <- entropy_gamma_sar(L, mu)
  output <- data.frame(
    SampleSize = integer(0),
    Estimator = character(0),
    TypeIErrorRate = numeric(0)
  )

  for (ssize in sample_sizes) {

    for (estimator_name in names(estimators)) {
      estimator <- estimators[[estimator_name]]
      reject_H0_count <- 0

      for (n_replication in 1:N) {

        #samples <- gi0_sample(mu, alpha, L, ssize)
        v.entropy <- numeric(R)
        for (r in 1:R) {

        samples <- gi0_sample(mu, alpha, L, ssize)

        if (grepl(" ", estimator_name)) {
          v.entropy[r] <- estimator(samples, B = B)
        } else {
          v.entropy[r] <- estimator(samples)
        }
      }

        mean_entropy <- mean(v.entropy)
      z_statistic <- sqrt(R) * (mean_entropy - true_entropy) / sd(v.entropy)
      p_value <- 2 * (1 - pnorm(abs(z_statistic)))
      alpha_t = 0.05

        reject_H0_count <- reject_H0_count + sum(p_value < 0.05)
      }

      typeI_error_rate <- reject_H0_count / (N)

      output <- rbind(
        output,
        data.frame(
          SampleSize = ssize,
          Estimator = estimator_name,
          TypeIErrorRate = round(typeI_error_rate, 5)
        )
      )
    }
  }

  colnames(output) <- c("$n$", "Estimator", "Type I Error Rate")

  return(output)
}

calculate_results_test_gi0_montecarlo <- function(sample_sizes, R, N, B, mu_values, alpha, L, estimators) {
  results_list <- list()

    results <- calculate_entropy_and_test_montecarlo(sample_sizes, R, N, B, mu_val, alpha, L, estimators)
    df <- as.data.frame(results)

results_gi0_1_montecarlo <- calculate_results_test_gi0_montecarlo(sample_sizes, R, N, B, mu_values, alpha, L, estimators)
#print(results_gi0_1_montecarlo)
save(results_gi0_1_montecarlo, file = "./Data/results_gi0_1_montecarlo.Rdata")

```{r Table_test_gi0_montecarlo, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
load("./Data/results_gi0_1_montecarlo.Rdata")

for (mu_val in mu_values) {
  results_data <- results_gi0_1_montecarlo[[as.character(mu_val)]]

  table_result <- kbl(
    results_data,
    caption = paste("Type I error with $L=5$, $\\mu=1$ and$\\alpha=\\infty$."),
    format = "latex",
    booktabs = TRUE,
    align = "c",
    escape = FALSE,
    digits = 4,
    label = "table_hipotesis_2"
  ) %>%
    collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle")

  #cat("### Results for mu =", mu_val, "\n")
  print(table_result)

```
Hypothesis test results were conducted with a \SI{95}{\percent} confidence level. 
The $Z$ statistic measures the discrepancy between the estimated entropy and the true entropy. 
The $p$-values associated with the $Z$ statistic are predominantly greater than $0.05$, for sample sizes above $25$, suggesting that the data are consistent with the null hypothesis.

>>>>

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE, cache=TRUE)
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(reshape2)
#library(plotly)
library(knitr)
library(pandoc)
library(gridExtra)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(rmutil)
library(invgamma)
library(tidyverse)
library(RColorBrewer)
library(ggsci)
#library(wesanderson)
library(ggpubr)
library(patchwork)
library(dplyr)
#options(kableExtra.latex.load_packages = FALSE)
library(devtools)
#devtools::install_github("haozhu233/kableExtra")
library(kableExtra)
library(ggthemes)
library(latex2exp)
library(e1071)# kurtosis
library(viridis)
library(nortest)# AD

@@

<!-- Fig.&nbsp;\ref{fig:3d_GIO} illustrates the entropy of $G_I^0$ distribution as a function of three key parameters: $\mu$, $\alpha$, and $L$. -->

<!-- ```{r 3d_GIO, fig.align="center",  out.width = "70%", fig.cap="The Shannon Entropy under ${G}_I^0$ models.", fig.show="hold",  fig.pos="hbt"} -->
<!-- knitr::include_graphics("../../../Figures/PDF/entropy_plot_3d.pdf") -->
<!-- ``` -->
<!-- As we explore the 3D plot, we can observe how changes in $\mu$, $\alpha$, and $L$ collectively influence the entropy of the $G_I^0$ distribution.  -->
<!-- We can identify regions where entropy is high or low, providing insights into the predictability and structure of the distribution in various regions of the parameter space. -->

@@

```{r Plot_GI0_to_gamma, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="$H_{ G_I^0}$ converges to the $H_{\\Gamma_{\\text{SAR}}}$ as $\\alpha$ takes large negative values and $L=8$."}

L <- c(8)
alphas <- c(  -3, -8, -20, -1000)
alpha_labels <- c( expression(italic(alpha) == -3), expression(italic(alpha) == -8), expression(italic(alpha) == -20), expression(italic(alpha) == -1000))

@@

```{r Plot_empirical, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Empirical distributions of $\\Gamma_{\\text{SAR}}$ and $G_I^0$ entropies as $\\mu=1$, $L=8$ and $\\alpha\\in\\{-1000, -20, -8, -3\\}$."}

@@

R <- 3000
mu <- 1
L <- 8
B <- 1
sample.size <- c( 121)

@@

@@

@@

estimators_to_plot <- c("Correa", "Ebrahimi", "Al Omari",  "Correa Bootstrap", "Ebrahimi Bootstrap", "Al Omari Bootstrap" )
  latex_estimator_names <- c("Correa" = expression("$\\widehat{italic(H)}_{C}$"),
                             "Correa Bootstrap" = expression("$\\widetilde{italic(H)}_{C}$"),
                            "Ebrahimi" = expression("$\\widehat{italic(H)}_{E}$"),
                            "Al Omari" = expression("$\\widehat{italic(H)}_{AO}$"),
                            "Ebrahimi Bootstrap" = expression("$\\widetilde{italic(H)}_{E}$"),
                            "Al Omari Bootstrap" = expression("$\\widetilde{italic(H)}_{AO}$"))
selected_estimators_latex <- latex_estimator_names[estimators_to_plot]

@@

colnames(reshaped_results) <- c("$\\mu$", "$n$", "$\\widetilde{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{E}}$", "$\\widetilde{H}_{\\text{AO}}$", "$\\widetilde{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{E}}$", "$\\widetilde{H}_{\\text{AO}}$")

#
print(
  kbl(
    reshaped_results,
    caption = "Bias and MSE of bootstrap estimators for $G_I^0$, $L=8$, $\\alpha=-20$.",
    format = "latex",
    booktabs = TRUE,
    align = "c",
    escape = FALSE, 
    digits = 3,  
    label = "table2"  
  ) %>%
    add_header_above(c(" ", " ", "Bias" = 3, "MSE" = 3)) %>%
    collapse_rows(columns = 1:2, latex_hline = "major", valign = "middle")
)
```

$$
 \begin{cases}\mathcal{H}_0: \mu_{\widetilde{H}}-\mu_{H}=0 \\ 
  \mathcal{H}_1:\mu_{\widetilde{H}}-\mu_{H}\neq0 .\end{cases}
$$
In other words, we verify the hypothesis that the data are fully-developed speckle.

For this purpose, we use the following test statistic:
\begin{equation}
\label{Eq:test_e}
S(\bm{Z};L_0)= \widetilde{H}(\bm{Z})-\left[H_{\Gamma_{\text{SAR}}}(L_0)+\ln \widebar{\bm{Z}}\right].
\end{equation}
This test statistic $S(\bm{Z};L_0)$ aims to assess the behavior of the data under the null hypothesis, through the empirical distribution of the test statistic values for a sample size of $n$. The density should center around zero if the test statistic is capable of detecting that the data are fully-developed speckle, i.e., $S(\bm{Z};L_0)\approx 0$. Otherwise, under the alternative hypothesis, the empirical distribution of the test statistic values is not centered around zero. This suggests significant differences and implies the presence of heterogeneous clutter.

## The Proposed Test
We analyze the finite sample size behavior of the test statistics defined in \eqref{Eq:test_e}.

Fig. \ref{fig:Plot_density} depicts empirical test statistic densities for various sample sizes, and Table \ref{tab:table_stat_combined} summarizes key statistics, including mean, SD, variance (Var), skewness, kurtosis, and Anderson–Darling $p$-values for normality. Results with $p$-values $> 0.05$  indicate no evidence against normality. 
Notably, small variance and near-zero skewness and kurtosis suggest limited spread, symmetry, and light tails, aligning with normal distribution expectations.

In Fig. \ref{fig:Plot_normality_qq}, normal QQ-plots visually affirm distributional similarity with the expected normal line, reinforcing our findings.

```{r Simulated_density, echo=FALSE, message=FALSE}
set.seed(1234567890, kind = "Mersenne-Twister")

R <- 1000
mu <- 1
B <- 2
alpha1 <- -8
sample.size <- c(50, 100, 150, 200, 250,300, 350)
L_values <- c(2, 5, 8, 18)

all_summary_stats <- list()
all_TestStatistics <- list()
all_TestNormality <- list()
all_plots <- list()

# For each L
for (L in L_values) {
  TestStatistics1 <- list()  
  summary_stats <- data.frame( LValue = character(),
                              SampleSize = numeric(),
                              Mean = numeric(),
                              SD = numeric(),
                              Variance = numeric(),
                              Skewness = numeric(),
                              Kurtosis = numeric(),
                              adpvalue = numeric()
                              )  # Nueva columna para  L
  # summary_normality <- data.frame(Sample_Size = numeric(),
  #                               lillie_p_value = numeric(),
  #                               ad_p_value = numeric())
  #normality_test <- list()#

  for (s in sample.size) {
    TestStat1 <- numeric(R)

    for (r in 1:R) {
      z <- gamma_sar_sample(L, mu, s)
      TestStat1[r] <- bootstrap_correa_estimator_log_mean(z, B) + (-L + log(L) - lgamma(L) - (1 - L) * digamma(L))
    }

    TestStatistics1[[as.character(s)]] <- data.frame("SampleSize" = rep(s, R), "Test_Statistics" = TestStat1)

    mean_val <- mean(TestStat1)
    sd_val <- sd(TestStat1)
    var_val <- var(TestStat1)
    skewness_val <- skewness(TestStat1)
    kurtosis_val <- kurtosis(TestStat1)
   # lillie_p_value <- lillie.test(TestStatistics1[[as.character(s)]]$Test_Statistics)$p.value
    ad_p_value <- ad.test(TestStatistics1[[as.character(s)]]$Test_Statistics)$p.value

    summary_stats <- rbind(summary_stats, data.frame(LValue = as.character(L),
                                                     SampleSize = s,
                                                     Mean = mean_val,
                                                     SD = sd_val,
                                                     Variance = var_val,
                                                     Skewness = skewness_val,
                                                     Kurtosis = kurtosis_val,
                                                     adpvalue = ad_p_value
                                                     ))

    # Almacenar resultados de normalidad
    # summary_normality <- rbind(summary_normality, data.frame(LValue = as.character(L),
    #                                                          SampleSize = s,
    #                                                          lilliepvalue = lillie_p_value,
    #                                                          adpvalue = ad_p_value))
  }

  all_TestStatistics[[as.character(L)]] <- TestStatistics1
  all_summary_stats[[as.character(L)]] <- summary_stats
  #all_TestNormality[[as.character(L)]] <- summary_normality

#save(all_TestStatistics, all_summary_stats, file = paste0("./Data/results_", L, ".Rdata"))
  save(all_TestStatistics, all_summary_stats, all_TestNormality, file = paste0("./Data/results_", L, ".Rdata"))
}

@@

```{r Plot_density, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Empirical density  under Gamma SAR model.", fig.width=6, fig.height=5}

theme_set(theme_minimal() +
            theme(text = element_text(family = "serif"),
                  legend.position = "bottom",
                  legend.text = element_text(angle = 0, vjust = 0.5)))

all_plots <- list()

for (L in L_values) {
  load(paste0("./Data/results_", L, ".Rdata"))

  combined_data <- do.call(rbind, all_TestStatistics[[as.character(L)]])
  combined_data$L <- L

  p <- ggplot(combined_data, aes(x = Test_Statistics, col = factor(SampleSize), linetype = factor(SampleSize))) +
    geom_line(stat = "density", linewidth = 1.0) +
    scale_color_viridis(discrete = TRUE, option = "C", direction = -1, begin = 0.1, end = 0.8, name = "Sample Size") +
    scale_linetype_manual(values = rep("solid", length(sample.size)), name = "Sample Size") +
    labs(x = "Test Statistics", y = "Density") +
    ggtitle(bquote(italic(L) == .(L))) +
    theme(plot.title = element_text(hjust = 0.5))#titulo centrado

  if (!any(L == L_values)) {
    p = p
  }

  all_plots[[as.character(L)]] <- p
}

combined_plot <- wrap_plots(all_plots, ncol = 2, nrow = 2) +
  plot_layout(guides = "collect")

print(combined_plot)

```{r Table_statistic, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

# for (L in L_values) {
#   summary_stats <- all_summary_stats[[as.character(L)]]
#   
#   print(summary_stats)
# }

# summary_stats_2 <- all_summary_stats[["2"]]

load("./Data/results_2.Rdata")
summary_stats_2 <- all_summary_stats[["2"]]

load("./Data/results_5.Rdata")
summary_stats_5 <- all_summary_stats[["5"]]

load("./Data/results_8.Rdata")
summary_stats_8 <- all_summary_stats[["8"]]

combined_summary_stats <- rbind(
  transform(summary_stats_2),
  transform(summary_stats_5),
  transform(summary_stats_8)

)
colnames(combined_summary_stats) <- c("$L$", "$n$", "Mean", "SD", "Var", "Skewness", "Kurtosis", "$p$-value")

# table
table_result_combined <- kbl(
  combined_summary_stats,
  caption = "Descriptive analysis of $S(Z)$ for different values of $L$, and $\\mu=1$.",
  format = "latex",
  booktabs = TRUE,
  align = "c",
  escape = FALSE,
  digits = 4,
  label = "table_stat_combined"
) %>%
  collapse_rows(latex_hline = "major", valign = "middle")# %>%
 # kable_styling(latex_options = c("striped", "hold_position"), full_width = FALSE)

print(table_result_combined)

```{r Plot_normality_qq, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Normal QQ-plots for  $n=100$.", fig.width=6, fig.height=5}

theme_set(theme_minimal() +
            theme(text = element_text(family = "serif"),
                  legend.position = "bottom",
                  legend.text = element_text(angle = 0, vjust = 0.5)))

# Cargar los resultados guardados
load("./Data/results_2.Rdata")
load("./Data/results_5.Rdata")
load("./Data/results_8.Rdata")
load("./Data/results_18.Rdata")

# Tamaño de muestra específico que deseas graficar
selected_sample_size <- 100

# Crear una lista para almacenar los ggplots
ggplot_list <- list()

# Para cada valor de L
for (L in c(2, 5, 8, 18)) {
  TestStatistics1 <- all_TestStatistics[[as.character(L)]]

  # Verifica si el tamaño de muestra seleccionado está disponible
  if (as.character(selected_sample_size) %in% names(TestStatistics1)) {
    p <- ggplot(TestStatistics1[[as.character(selected_sample_size)]], 
                aes(sample = Test_Statistics)) +
      geom_qq(col = "blue", shape = 20) +
      geom_qq_line(col = "darkgreen", linetype = 2) +
      labs(title = bquote(italic(L) == .(L)),
           x = "Theoretical Quantiles",
           y = "Sample Quantiles") +
      theme(plot.title = element_text(hjust = 0.5))#titulo centrado

    ggplot_list[[as.character(L)]] <- p
  } else {
    warning(paste("No size sample", selected_sample_size, " L =", L))
  }
}
combined_plot1 <- wrap_plots(ggplot_list, ncol = 2, nrow = 2) +
  plot_layout(guides = "collect")

print(combined_plot1)

# }

@@

  plot <- ggplot(TestStatistics1, aes(x = Test_Statistics)) +
    geom_line(aes(col = factor(Sample_Size), linetype = factor(Sample_Size)), stat = "density", linewidth = 1.0) +
    geom_line(data = TestStatistics2, aes(x = Test_Statistics2), stat = "density", color = "blue", linetype = "dashed", linewidth = 1) +
    geom_vline(xintercept = difference.betweeen.GammaSAR.GI0.n.Look(-8, 5), col="darkgreen", linetype = "dotted", linewidth = 0.6) +
    annotate("text", x=difference.betweeen.GammaSAR.GI0.n.Look(-8, 5), y=7, parse=TRUE, label="alpha==-8", hjust=-.1, vjust=1.0, col="darkgreen") +
    geom_vline(xintercept = difference.betweeen.GammaSAR.GI0.n.Look(-1000, 5), col="darkgreen", linetype = "dotted", linewidth = 0.6) +
    theme_minimal() +
    theme(
      text = element_text(family = "serif"),
      legend.position = "none"  
    )

@@
